# Data sources

- Challenges
- Data sources
- Dataset and columns explanation

```{r message=FALSE, warning=FALSE}
library(naniar)
library(tidyverse)
library(readr)
library(maptools)
library(ggmap)
library(ggrepel)
library(lubridate)
library(ggplot2)
library(gridExtra)
library(grid)
library(ggpubr)
library(cowplot)
```

```{r message=FALSE, warning=FALSE}
data <- read_csv("dataset/MVC_split.csv")
```

Let's see how our dataset looks like, it's a huge dataset with 29 variables and over 1.6 million rows. 

```{r}
head(data)
```

We might need to use a sample of the data in some places. Let's have a look at the sample of 50,000 rows.

```{r}
dim(data_sample)
```

```{r}
head(data_sample)
```

```{r}
colnames(data_sample)
```

![]("")

```{r message=FALSE, warning=FALSE}
api_key = "AIzaSyBiUv8OS_lQQyxfz5ljAl2MaUUqJgKK_F8"
```

This project explores the more recent data from NYC Open Data for Motor vehicle Collisions[Data Set](https://data.cityofnewyork.us/Public-Safety/NYPD-Motor-Vehicle-Collisions/h9gi-nx95).

This dataset can also be reached and interacted with through its [Google BigQuery location](https://bigquery.cloud.google.com/table/bigquery-public-data:new_york.nypd_mv_collisions?tab=schema)

