<<<<<<< HEAD
=======
---
output: html_document
editor_options: 
chunk_output_type: console
---

# Data transformation

- Th. date split


******* image (location) - explain how got coords *******


```{r message=FALSE, warning=FALSE}
# MAIN CLEANED DATA
missing_data <- subset(data,  is.na(LATITUDE) | is.na(LONGITUDE) | (LATITUDE >= 40.496942  & LONGITUDE >= -74.258905 & LATITUDE <= 40.882507  & LONGITUDE <= -73.789791))

data <- subset(data, (LATITUDE >= 40.496942  & LONGITUDE >= -74.258905 & LATITUDE <= 40.882507  & LONGITUDE <= -73.789791))
```

```{r message=FALSE, warning=FALSE}
data_sample <- sample_n(data,50000, set.seed=69)
```


- dates factors

```{r message=FALSE, warning=FALSE}
#Converting the categorical columns into factors
cols_to_be_factors = c(3, 7:10, 19:23)

data[cols_to_be_factors] = lapply(data[cols_to_be_factors], factor)
data_sample[cols_to_be_factors] = lapply(data_sample[cols_to_be_factors], factor)
```

```{r message=FALSE, warning=FALSE}
#Converting the Date column into Date class.
data$`ACCIDENT DATE` = as.Date(data$`ACCIDENT DATE`)
data_sample$`ACCIDENT DATE` = as.Date(data_sample$`ACCIDENT DATE`)
```

- save clean data




>>>>>>> c176b0af6430ce29b5533f880314e8d7896cb374
